Reproducibility and plant pathology: where do we stand and a way forward

### 2021-06-17 analysis/paper/paper.Rmd
Update figure size

# put them all together
p <- (i | ii) / (iii | iv)
p <- p + plot_annotation(tag_levels = "i")
ggsave(filename = "../figures/Sparks et al Figure 2.eps",
       plot = p,
       device = "eps")
extrafont::embed_fonts(
   file = ("../figures/Sparks et al Figure 2.eps"),
   outfile = ("figures/Sparks et al Figure 2.eps"),
   options = "-dEPSCrop"
)
knitr::include_graphics(path = "../figures/Sparks et al Figure 2.eps")
```

>>>>

# put them all together
p <- (i | ii) / (iii | iv)
p <- p + plot_annotation(tag_levels = "i")
ggsave(filename = "../figures/Sparks et al Figure 2.eps",
       plot = p,
       device = "eps",
       width = 6,
       height = 6,
       units = "in")
extrafont::embed_fonts(
   file = ("../figures/Sparks et al Figure 2.eps"),
   outfile = ("figures/Sparks et al Figure 2.eps"),
   options = "-dEPSCrop"
)
knitr::include_graphics(path = "../figures/Sparks et al Figure 2.eps")
```
